### 2023-06-19 README.Rmd
updated logo, documentation, prior arguments added for Bayesian methods,  rearranged informed t test functions in R folder
updated logo path
added citation cff and updated readme with citations

# SampleSizePlanner

@@

## Available sample size planning methods
* Two One‐Sided Tests (TOST)
* Interval Equivalence Bayes factor
* Classical power analysis
* Power curve
* Bayes Factor Design Analysis (BFDA)
* Predetermined sample size with Bayes factor
* Accuracy In Parameter Estimation (AIPE)
* A-priori precision (APP)
* Region of Practical Equivalence (ROPE)

@@

## Note

The tutorial paper that presents the web application and R package is not reviewed yet. More details are available in Kovacs, van Ravenzwaaij, Hoekstra & Aczel (2021).

>>>>

# SampleSizePlanner <a href='https://marton-balazs-kovacs.github.io/SampleSizePlanner/'><img src='man/figures/ssp_logo.png' align="right" height="200" /></a>

@@

## Available sample size planning methods
* Two One‐Sided Tests (TOST)
* Interval Equivalence Bayes factor
* Classical power analysis
* Power curve
* Bayes Factor Design Analysis (BFDA)
* Predetermined sample size with Bayes factor
* Accuracy In Parameter Estimation (AIPE)
* A-priori precision (APP)
* Region of Practical Equivalence (ROPE)
* Non-inferiority Bayes factor

@@

The tutorial paper for two-group study designs can be found [HERE](https://journals.sagepub.com/doi/pdf/10.1177/25152459211054059).

## Citation

Please cite `SampleSizePlanner` if you use it for determining your sample size. To cite SampleSizePlanner the software, use:

```{r echo = FALSE, results = "asis"}
print(citation("SampleSizePlanner"), style = "text")
```

Or copy the reference information to your BibTeX file:

~~~bibtex

```{r echo = FALSE, results = "asis"}
print(citation("SampleSizePlanner"), style = "Bibtex")
```

~~~

To cite the tutorial paper on two-group designs use:

Kovacs, M., van Ravenzwaaij, D., Hoekstra, R., & Aczel, B. (2022). SampleSizePlanner: A tool to estimate and justify sample size for two-group studies. _Advances in Methods and Practices in Psychological Science, 5_(1), 25152459211054059.
